Predicting maintenance patterns

### 2019-10-11 R/presentations/DISC_201909/presentation.Rmd

* Number of instances: small (5000), medium (1000) and large (1000).
* Time limit at 3600 seconds.
* We seeded instance generation for better comparison.
* CPLEX running 1 thread.

Large instances have:

* 45 aircraft
* 90 months
* +20 missions (3 active missions at any given time).

@@

Better solutions, more solutions.

@@

* in ~85% of instances we outperformed base model.
* ~105% average gain in objective function.
* ~18% less time in average to solve.
]

>>>>

* Number of instances: small (5000), medium (1000) and large (1000) and very large (1000).
* Time limit at 3600 seconds.
* We seeded instance generation for better comparison.
* CPLEX running 1 thread.

Largest instances have:

* 60 aircraft
* 90 months
* ~30 missions (4 active missions at any given time).

@@

Faset solutions, more solutions. (Large instances aggresive cuts).

@@

* +75% worse solutions (caveat).
* most solutions are between 0-5% of best known.
* ~18% less time in average to solve.
* ~53% less time to "optimal".
]
